---
title: "Publications"
toc: true
toc-depth: 2
---

```{r metrics}
#| echo: false
#| message: false
#| warning: false
#| results: asis

# Publication lists live in data/publications.yml and are rendered by
# R/pubs.R (edit the YAML, not this page).
source("R/pubs.R")
n_pr      <- pubs_count("peer_reviewed")
n_inpress <- pubs_count("in_press")
n_inrev   <- pubs_count("in_review")
n_inprep  <- pubs_count("in_preparation")

# Read cached scholarship metrics -- the same file cv.qmd uses
# (refresh via Rscript scripts/fetch_metrics.R)
m <- tryCatch(yaml::read_yaml("assets/metrics.yml"), error = function(e) NULL)
cites   <- if (!is.null(m$scholar$citations_total)) m$scholar$citations_total else NA
h_index <- if (!is.null(m$scholar$h_index))         m$scholar$h_index         else NA
updated <- if (!is.null(m$last_checked))            m$last_checked            else NA

cat('<div class="metrics-row">\n')
cat(sprintf('<div class="metric"><span class="num">%d</span><span class="label">Peer-reviewed</span></div>\n', n_pr))
if (n_inpress > 0) cat(sprintf('<div class="metric"><span class="num">%d</span><span class="label">In press</span></div>\n', n_inpress))
cat(sprintf('<div class="metric"><span class="num">%d</span><span class="label">In review</span></div>\n', n_inrev))
cat(sprintf('<div class="metric"><span class="num">%d</span><span class="label">In preparation</span></div>\n', n_inprep))
if (!is.na(cites))   cat(sprintf('<div class="metric"><span class="num">%s</span><span class="label">Citations</span></div>\n', format(cites, big.mark = ",")))
if (!is.na(h_index)) cat(sprintf('<div class="metric"><span class="num">%d</span><span class="label">h-index</span></div>\n', h_index))
cat('</div>\n')

if (!is.na(updated)) {
  cat(sprintf('<p class="metrics-foot">Citations and h-index from <a href="https://scholar.google.com.br/citations?user=qDwcLvIAAAAJ" target="_blank">Google Scholar</a>, last updated %s.</p>\n',
              updated))
} else {
  cat('<p class="metrics-foot">Live citation count on <a href="https://scholar.google.com.br/citations?user=qDwcLvIAAAAJ" target="_blank">Google Scholar</a>.</p>\n')
}
```

::: {.callout-note appearance="minimal"}
<u>Underline</u> = supervised student.
Icons: <i class="fa-solid fa-file-pdf"></i> PDF · <i class="ai ai-biorxiv"></i> bioRxiv preprint · <i class="ai ai-open-access"></i> other open-access preprint · <i class="ai ai-open-data"></i> open data · <i class="ai ai-doi"></i> DOI · <i class="fa-solid fa-database"></i> data repository · <i class="fa-solid fa-file-powerpoint"></i> slides · <i class="fa-solid fa-image"></i> poster · <i class="fa-solid fa-file-lines"></i> abstract · <i class="fa-solid fa-flask"></i> protocol.
:::

## Peer-reviewed articles

::: {.pub-list}

```{r pubs-peer-reviewed}
#| echo: false
#| results: asis
pubs_list("peer_reviewed")
```

:::

## Books

```{r pubs-books}
#| echo: false
#| results: asis
pubs_list("books")
```

## Book chapters

```{r pubs-chapters}
#| echo: false
#| results: asis
pubs_list("book_chapters")
```

## In press

```{r pubs-in-press}
#| echo: false
#| results: asis
pubs_list("in_press")
```

## In review

```{r pubs-in-review}
#| echo: false
#| results: asis
pubs_list("in_review")
```

## In preparation

```{r pubs-in-prep}
#| echo: false
#| results: asis
pubs_list("in_preparation")
```

## Conference abstracts

### 2023

Severgnini, M.R.; **PROVETE, D.B.** 2023. It's about time: the effects of
urbanization on phenotypic traits in a tropical city.
[Poster, 108th Annual Meeting of the ESA, Portland, OR, USA]. &nbsp;
<a href="https://esa2023.eventscribe.net/fsPopup.asp?PosterID=588896&amp;Query=provete&amp;Mode=posterinfo" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2022

Moroti, M.T.; da Silva, F.R.; **PROVETE, D.B.** 2022. Non-equilibrium
processes prevail in shaping species richness and functional diversity of
terrestrial vertebrates in a global hotspot.
[Poster, 107th Annual Meeting of the ESA, Montréal, QC, Canada]. &nbsp;
<a href="https://programarchives.z20.web.core.windows.net/2022/Paper2155661.html" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Acero-Murcia, A.C.; Fischer, E.A.; **PROVETE, D.B.** 2022. Landscape
composition and structure as a filter to wing shape in a tropical bat
metacommunity.
[Poster, 2022 British Ecological Society Annual Meeting, Edinburgh, UK].

### 2021

Acero-Murcia, A.C.; Severgnini, M.R.; Lacerda, H.D.; Fischer, E.A.;
**PROVETE, D.B.** 2021. The influence of diet and foraging strategy in the
skull morphology in a bat community.
[Oral, I Simpósio Brasileiro de Morfologia Comparada de Vertebrados,
Brasília].
*Honorable mention — Best oral presentation.* &nbsp;
<a href="https://proceedings.science/simorf-2021/papers/the-influence-of-diet-and-foraging-strategy-in-the-skull-morphology-in-a-bat-community" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Severgnini, M.R.; Baldo, D.; Vera Candioti, M.F.; **PROVETE, D.B.** 2021.
Influência do ambiente sobre a forma de corpo em girinos do gênero
*Melanophryniscus* (Anura: Bufonidae).
[Poster, I Simpósio Brasileiro de Morfologia Comparada de Vertebrados,
Brasília]. *Honorable mention — Best poster.* &nbsp;
<a href="https://proceedings.science/simorf-2021/papers/influencia-do-ambiente-sobre-a-forma-de-corpo-em-girinos-do-genero-melanophryniscus--anura--bufonidae-" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Martins, B.O.; Franco-Belussi, L.; Fernandes, C.E.; **PROVETE, D.B.** 2021.
Evolução do formato de células vermelhas sanguíneas numa radiação
continental de peixes.
[Oral, I Simpósio Brasileiro de Morfologia Comparada de Vertebrados,
Brasília]. *Honorable mention — Best oral presentation.* &nbsp;
<a href="https://proceedings.science/simorf-2021/papers/evolucao-do-formato-de-celulas-vermelhas-sanguineas-numa-radiacao-continental-de-peixes" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a> · &nbsp;
<a href="https://f1000research.com/posters/8-1700" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="talks/2021-simorf-red-blood-cell-shape.pdf" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-pdf"></i></a>

### 2019

Bonin, L.; Soares, P.; Eriksson, A.; **PROVETE, D.B.** 2019. Evolution of
echolocation in bats (Chiroptera). *F1000Research* 8:1201.
[Poster, X Congresso Brasileiro de Mastozoologia]. *Best poster presentation.* &nbsp;
<a href="https://doi.org/10.7490/f1000research.1117133.1" title="DOI: 10.7490/f1000research.1117133.1" aria-label="DOI"><i class="ai ai-doi"></i> 10.7490/f1000research.1117133.1</a>

Martins, B.O.; **PROVETE, D.B.**; Franco-Belussi, L.; Fernandes, C.E.S.
2019. Evolution of red cell shape in a continental radiation of fishes.
*F1000Research* 8:1700.
[Poster, IX Jornada da Biologia, in Portuguese].
*Best poster presentation.* &nbsp;
<a href="https://doi.org/10.7490/f1000research.1117527.1" title="DOI: 10.7490/f1000research.1117527.1" aria-label="DOI"><i class="ai ai-doi"></i> 10.7490/f1000research.1117527.1</a>

Severgnini, M.R.; Souza, V. dos S.; Santana, D.; **PROVETE, D.B.** 2019.
The tempo and mode of Neotropical tadpoles body shape evolution.
*F1000Research* 8:1181.
[Poster, IX Congresso Brasileiro de Herpetologia]. &nbsp;
<a href="https://doi.org/10.7490/f1000research.1117116.1" title="DOI: 10.7490/f1000research.1117116.1" aria-label="DOI"><i class="ai ai-doi"></i> 10.7490/f1000research.1117116.1</a>

Duarte, R.G.; Almeida, W.; **PROVETE, D.B.**; Avila, R.; Teles, D.A.;
Ribeiro, S. 2019. Da lama ao caos: qual a influência dos lixões na relação
entre endoparasitas e o "sapo cururu", *Rhinella jimi* (Stevaux, 2002)?
[Anais do IX Congresso Brasileiro de Herpetologia]. &nbsp;
<a href="https://proceedings.science/cbh-2019/papers/da-lama-ao-caos--qual-a-influencia-dos-lixoes-na-relacao-entre-endoparasitas-e-o----sapo-cururu-----rhinella-jimi--steva" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Ganci, C.; Dudczak, A.; **PROVETE, D.B.** 2019. Influência da temperatura
no tempo de resposta e distância de salto em *Lysapsus limellum*
(Anura: Hylidae). [Anais do IX Congresso Brasileiro de Herpetologia]. &nbsp;
<a href="https://proceedings.science/cbh-2019/papers/influencia-da-temperatura-no-tempo-de-resposta-e-distancia-de-salto-em-lysapsus-limellum--anura--hylidae--" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2017

**PROVETE, D.B.** 2017. La evolución de la pigmentación interna en anfibios
anuros neotropicales.
[Oral, invited symposium, Congreso Argentino de Herpetología, Salta, Argentina]. &nbsp;
<a href="https://f1000research.com/slides/6-1952" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a>

Silva, F.R.; **PROVETE, D.B.**; Gerassi, L.; Bovo, R.P. 2017. What do data
from fieldwork and scientific collections tell us about species richness and
composition of amphibians and reptiles?
[Poster, VIII Congresso Brasileiro de Herpetologia, Campo Grande, Brazil]. &nbsp;
<a href="https://proceedings.science/cbh/trabalhos/what-do-data-from-fieldwork-and-scientific-collections-tell-us-about-species-ric?lang=pt-br" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Ribeiro, S.; **PROVETE, D.B.**; Almeida, W.; Colli, G.; Pianka, E.;
Mesquita, D.O. 2017. Estrutura da comunidade de lagartos no Cerrado relictual
da Chapada do Araripe, nordeste do Brasil.
[Oral, VIII Congresso Brasileiro de Herpetologia, Campo Grande, Brazil]. &nbsp;
<a href="https://proceedings.science/cbh/trabalhos/estrutura-da-comunidade-de-lagartos-no-cerrado-relictual-da-chapada-do-araripe-n?lang=pt-br" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2015

Leite, G.B.; Franco-Belussi, L.; **PROVETE, D.B.**; Oliveira, C. 2015.
Evolution of a reproductive character in 26 Neotropical anuran species.
[Oral, VII Encontro de Biologia Comparada, Ribeirão Preto, Brazil]. &nbsp;
<a href="http://f1000research.com/slides/4-458" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a>

### 2014

Leite, G.B.; Franco-Belussi, L.; **PROVETE, D.B.**; Oliveira, C. 2014.
Comparative analysis of testicular histology in eight species of frogs.
[Poster, XV Congreso Argentino de Herpetología, Mendoza, Argentina]. &nbsp;
<a href="assets/abstracts/2014-leite-cah.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2013

Garey, M.V.; **PROVETE, D.B.**; Haddad, C.F.B.; Rossa-Feres, D.C. 2013.
The role of environmental and spatial gradients on a pond-dwelling anuran
metacommunity dynamics.
[Poster, XIV Congresso Argentino de Herpetología, Puerto Madryn, Argentina]. &nbsp;
<a href="https://f1000research.com/posters/1094401" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2013-garey-cah.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Rossa-Feres, D.C.; Jordani, M.X.; **PROVETE, D.B.** 2013. Niche divergence
and environmental filtering regulate the assembly of a Neotropical larval
anuran metacommunity.
[Poster, 98th Annual Meeting of the ESA, Minneapolis, MN, USA]. &nbsp;
<a href="https://f1000research.com/posters/1094038" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="https://programarchives.z20.web.core.windows.net/2013/Paper44837.html" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Loyola, R.D.; Lemes, P.; Brum, F.T.; **PROVETE, D.B.**; Duarte, L.D.S. 2013.
Clade-specific consequences of climate change to amphibians in Atlantic
Forest protected areas.
[Poster, 98th Annual Meeting of the ESA, Minneapolis, MN, USA]. &nbsp;
<a href="https://f1000research.com/posters/1093889" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="https://programarchives.z20.web.core.windows.net/2013/Paper44628.html" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

**PROVETE, D.B.**; Franco-Belussi, L.; Santos, L.R.S.; Zieri, R.;
Moresco, R.M.; Almeida, S.C.; Martins, I.A.; Oliveira, C. 2013. Phylogenetic
signal and diversity of visceral pigmentation in eight anuran families.
[Oral, 2013 Joint Meeting of Ichthyologists and Herpetologists, Albuquerque,
NM, USA]. &nbsp;
<a href="http://www.slideshare.net/provete/phylogenetic-signal-and-diversity-of-visceral-pigmentation-in-eight-anuran-families-24316658" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a> · &nbsp;
<a href="assets/abstracts/2013-provete-jmih.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2012

**PROVETE, D.B.**; Gonçalves-Souza, T.; Garey, M.V.; Martins, I.A.;
Rossa-Feres, D.C. 2012. Fine-scale spatial patterns and pond morphology
jointly affect metacommunity structure of Neotropical tadpoles.
[Oral, 49th Meeting of the Association for Tropical Biology and
Conservation, Bonito, Brazil]. &nbsp;
<a href="http://www.slideshare.net/provete/finescale-spatial-patterns-and-pond-morphology-jointly-affect-metacommunity-structure-of-neotropical-tadpoles" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a> · &nbsp;
<a href="assets/abstracts/2012-provete-atbc-fine-scale.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

**PROVETE, D.B.** 2012. Phylogenies help to uncover diversity patterns in
Neotropical amphibians.
[Oral, 49th Meeting of the Association for Tropical Biology and
Conservation, Bonito, Brazil]. &nbsp;
<a href="http://www.slideshare.net/provete/phylogenies-help-to-uncover-diversity-patterns-in-neotropical-amphibians" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a> · &nbsp;
<a href="assets/abstracts/2012-provete-atbc-phylogenies.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Villalobos, F.; **PROVETE, D.B.**; Gouveia, S.F.; Dobrovolski, R. 2012. Rich
and rare ain't the common share: describing biodiversity and informing
conservation practices for South American amphibians.
[Poster, 49th Meeting of the Association for Tropical Biology and
Conservation, Bonito, Brazil]. &nbsp;
<a href="assets/abstracts/2012-villalobos-atbc.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Oliveira, C.; Franco-Belussi, L.; **PROVETE, D.B.**; Santos, L.R.S.;
Zieri, R.; Moresco, R.M. 2012. Visceral pigmentation in anurans: an
important morphological character for phylogenetic analyses.
[Poster, XXII International Symposium on Morphological Sciences,
São Paulo, Brazil]. &nbsp;
<a href="assets/abstracts/2012-oliveira-morphological-sciences.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2011

**PROVETE, D.B.**; Garey, M.V.; Rossa-Feres, D.C.; Martins, I.A. 2011.
Padrões de abundância e distribuição espacial numa metacomunidade de
girinos ao longo de um gradiente de cobertura de dossel.
[Oral, IX Congresso Latino-Americano de Herpetologia, Curitiba, Brazil]. &nbsp;
<a href="http://slidesha.re/oQnawd" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a> · &nbsp;
<a href="assets/abstracts/2011-provete-clah.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Silva, V.X.; Sacramento, M.A.; **PROVETE, D.B.** 2011. Análise preliminar
da biodiversidade herpetofaunística sul mineira no contexto do Programa
Biota Minas.
[Poster, IX Congresso Latino-Americano de Herpetologia, Curitiba, Brazil]. &nbsp;
<a href="assets/abstracts/2011-silva-clah.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Negri, D.; **PROVETE, D.B.**; Laporta, J. 2011. Estrutura de comunidade de
anfíbios anuros na fase larval em ambientes lóticos e lênticos em
Paranapiacaba, Santo André, São Paulo.
[Poster, IX Congresso Latino-Americano de Herpetologia, Curitiba, Brazil]. &nbsp;
<a href="https://f1000research.com/posters/1094207" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2011-negri-clah.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

**PROVETE, D.B.**; Gonçalves-Souza, T.; Rossa-Feres, D.C.; Martins, I.A.
2011. Predaceous insects do not influence space use by anuran larvae: the
role of environment and scale.
[Oral, 96th Annual Meeting of the ESA]. &nbsp;
<a href="http://slidesha.re/oo0rkW" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a> · &nbsp;
<a href="https://programarchives.z20.web.core.windows.net/2011/Paper30898.html" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

**PROVETE, D.B.**; Rossa-Feres, D.C.; Martins, I.A. 2011. Partilha de nicho
em comunidades de girinos de ambientes lênticos.
[Poster, 63rd Annual Meeting of the Brazilian Society for the Advancement
of Science, Goiânia, Brazil]. &nbsp;
<a href="https://f1000research.com/posters/2085" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2011-provete-sbpc.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2010

**PROVETE, D.B.** 2010. Chondrocrania of frog larvae of the genus
*Physalaemus* and their relatives.
[Oral, 9th ICVM, Punta del Este, Uruguay]. &nbsp;
<a href="http://slidesha.re/fTwYIe" title="Slides" aria-label="Slides"><i class="fa-solid fa-file-powerpoint"></i></a> · &nbsp;
<a href="assets/abstracts/2010-provete-icvm.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2009

**PROVETE, D.B.**; Garey, M.V.; Rossa-Feres, D.C. 2009. Descrição do girino
e do canto de anúncio de *Physalaemus barrioi* Bokermann, 1967
(Anura: Leiuperidae).
[Poster, IV Congresso Brasileiro de Herpetologia, Pirenópolis, Brazil]. &nbsp;
<a href="https://f1000research.com/posters/853" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a>

### 2007

**PROVETE, D.B.**; Sacramento, M.A.; Silva, V.X. 2007. Intra- and
interspecific relationships between tadpoles and insects in a temporary
pond, southeastern Brazil.
[Poster, III Congresso Brasileiro de Herpetologia, Belém, Brazil]. &nbsp;
<a href="https://f1000research.com/posters/832" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2007-provete-cbh.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Sacramento, M.A.; **PROVETE, D.B.**; Silva, V. 2007. Descrição da biologia
reprodutiva de *Phasmahyla cochranae*.
[Poster, III Congresso Brasileiro de Herpetologia, Belém, Brazil]. &nbsp;
<a href="https://f1000research.com/posters/1094221" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2007-sacramento-cbh.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

### 2006

**PROVETE, D.B.**; Sacramento, M.A.; Silva, V.X. 2006. Relações tróficas
entre taxocenoses de girinos (Amphibia: Anura) e insetos em poças
temporárias na Fazenda Experimental de Lambari-MG.
[Poster, 14º Simpósio Internacional de Iniciação Científica da USP,
Ribeirão Preto]. &nbsp;
<a href="https://f1000research.com/posters/1094199" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2006-provete-siicusp.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

Sacramento, M.A.; **PROVETE, D.B.**; Silva, V.X. 2006. Uso da vegetação por
*Phasmahyla cochranae* (Amphibia, Anura) para confecção de ninhos no Parque
Estadual de Nova Baden, Lambari-MG.
[Poster, 14º Simpósio Internacional de Iniciação Científica da USP,
Ribeirão Preto]. &nbsp;
<a href="https://f1000research.com/posters/1094222" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2006-sacramento-siicusp.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

**PROVETE, D.B.**; Sturaro, M.J.; Sacramento, M.A.; Oliveira, P.B.B.;
Dias, P.H.F.; Rodrigues, R.C.; Gaiga, R.J.; Silva, V.X. 2006. Dados
preliminares sobre diversidade e uso de microhabitat por uma taxocenose de
anfíbios num brejo na área urbana de Alfenas-MG.
[Poster, II Jornada de Iniciação Científica de Alfenas, Alfenas, Brazil]. &nbsp;
<a href="https://f1000research.com/posters/1094198" title="Poster" aria-label="Poster"><i class="fa-solid fa-image"></i></a> · &nbsp;
<a href="assets/abstracts/2006-provete-jic-alfenas.pdf" title="Abstract" aria-label="Abstract"><i class="fa-solid fa-file-lines"></i></a>

## Master's thesis

**PROVETE, D.B.** 2010. *Uso de recursos e padrão de co-ocorrência com
insetos predadores em comunidades sub-tropicais de girinos* [main text in
English, introduction in Portuguese]. Master's thesis. &nbsp;
<a href="https://web.archive.org/web/20230327072411/https://www.lap-publishing.com/catalog/details/store/gb/book/978-3-8465-1727-7/diversity-and-resource-use-in-a-neotropical-tadpole-metacommunity" title="Available as a book" aria-label="Available as a book"><i class="fa-solid fa-book"></i> Available as a book</a>.
